\documentclass[12pt,-letter paper]{article}    
\usepackage{gvv-book}   
\usepackage{gvv}
\begin{document}
\begin{enumerate}
\item Write the position vector of the point which divides the join of points with position vectors $ \overrightarrow{3a} - \overrightarrow{2b}$ and $\overrightarrow{2a}+\overrightarrow{3b}$ in the ratio $2:1$.
\item Write the number of vectors of unit length perpendicular to both the vectors
	$\overrightarrow{a} = 2\hat{i} + \hat{j} + 2\hat{k}$  and $\overrightarrow{b} = \hat{j} + \hat{k}$.
\item Find the vector equation of the plane with intercepts $3$, $- 4$, and $2$ on the $x$, $y$ and $z$-axis, respectively.
\item If $x$ $\epsilon$ $N$ and $\mydet{x+3 & -2 \\ -3x & 2x}=8$, then find the value of $x$.
\item Use elementary column operation $C_2 \rightarrow C_{2}+2C_{1}$ in the following  matrix  equation:\\ $\myvec{2 & 1 \\  2 & 0}=\myvec{3 & 1 \\ 2 & 0}\myvec{1 & 0 \\ -1 & 1}$
\item  Write the number of all possible matrices of order \(2\times 2\) with each entry $1$,$2$ or $3$.
\item Evaluate : 
\begin{align} 
\int_{0}^{\frac{\pi}{2}} \frac{\sin^2 x}{\sin x + \cos x} \, dx
\end{align}
\item Evaluate :
\begin{align}
\int_{0}^\frac{3}{2}\left| x \cos \pi x \right| \, dx
\end{align}
\item In a game, a man wins \rupee $ 5$  for getting a number greater than $4$ and loses \rupee $1$ otherwise, when a fair die is thrown. The man decided to throw a die thrice but to quit as and when he gets a number greater than $4$. Find the expected value of the amount he wins/loses.
\item  A bag contains $4$ balls. Two balls are drawn at random (without replacement) and are found to be white. What is the probability that all balls in the bag are white?
\item Find :                    
\begin{align}                                    
\int \frac{x^2}{x^4 + x^2 - 2} \, dx   
\end{align}
\item If $ x=a \sin 2t (1 + \cos 2t)$ and $ y=b \cos 2t (1 - \cos 2t)$, find $\frac{dy}{dx}$ at $ t = \frac{\pi}{4}$.
\item Find the coordinates of the point where the line through the points $ A(3,4,1) $ and $B(5,1,6)$ crosses the $XZ$ plane. Also find the angle which this line make with the $XZ$ plane.
\item Find :
\begin{align}  
\int (3x+1)\sqrt {4-3x-2x^2} \ dx    
\end{align}

\item The equation of tangent at $(2,3)$ on the curve $y^2=ax^3+b$ is $y=4x-5$. Find the values of $a$ and $b$.            
\item A trust invested some money in two type of bonds. The first bond pays $10\percentage$ interest and second bond pays $12\percentage$ interest. The trust received  $\rupee2,800$ as interest. However, if trust had interchanged money in bonds, they would have got  $\rupee 100$ less as interest. Using matrix method, find the amount invested by the trust. Interest received on this amount will be given to Helpage India as donation. Which value is reflected in this question?
\end{enumerate}
\end{document}

